Whole-body connectome of a segmented annelid larva

### 2024-08-16 Manuscript.tex
Revision: change outgoing, incoming to post- presyn in figs and text, add refs

\title{Whole-body connectome of a segmented annelid larva}
\author{}
\date{}

@@

\setstretch{1.2}
\hfill\break

Gáspár Jékely\textsuperscript{1,2,*} , Sanja Jasek\textsuperscript{1,2},
Martin Gühmann\textsuperscript{3}, Luis Alberto Bezares
Calderón\textsuperscript{2}, Elizabeth A. Williams\textsuperscript{4},
Réza Shahidi\textsuperscript{5}\\

\textsuperscript{1}Heidelberg University, Centre for Organismal Studies
(COS), 69120 Heidelberg, Germany\\
\textsuperscript{2}Living Systems Institute, University of Exeter,
Exeter, EX4 4QD, United Kingdom\\
\textsuperscript{3}School of Biological Sciences, University of Bristol,
Bristol, United Kingdom\\
\textsuperscript{4}BioSciences, University of Exeter, Stocker Road,
Exeter EX4 4QD, Exeter, United Kingdom\\
\textsuperscript{5}Electron Microscopy Core Facility (EMCF), University
of Heidelberg, 69120 Heidelberg, Germany\\
\textsuperscript{*}Correspondence: gaspar.jekely@cos.uni-heidelberg.de

\section{Abstract}\label{abstract}

>>>>

\title{Whole-body connectome of a segmented annelid larva}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\raggedright

Csaba Verasztó\textsuperscript{1,2†}, Sanja
Jasek\textsuperscript{1,3,†}, Martin Gühmann\textsuperscript{4}, Luis
Alberto Bezares-Calderón\textsuperscript{1}, Elizabeth A.
Williams\textsuperscript{5}, Réza Shahidi\textsuperscript{6}, Gáspár
Jékely\textsuperscript{1,3,*} \newline\textsuperscript{1}Living Systems
Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom
\newline\textsuperscript{2}École Polytechnique Fédérale de Lausanne
(EPFL), Lausanne, Switzerland, \textsuperscript{3}Heidelberg University,
Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline
\newline\textsuperscript{4}School of Biological Sciences, University of
Bristol, Bristol, United Kingdom \newline\textsuperscript{5}BioSciences,
University of Exeter, Stocker Road, Exeter EX4 4QD, Exeter, United
Kingdom\newline \textsuperscript{6}Electron Microscopy Core Facility
(EMCF), University of Heidelberg, 69120 Heidelberg, Germany \newline
\textsuperscript{*}Correspondence: gaspar.jekely@cos.uni-heidelberg.de
\newline \textsuperscript{†}These authors contributed equally to this
work}
\author{}
\date{}

@@

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\setstretch{1.2}
\section{Abstract}\label{abstract}
